---
title: "klabs"
author: "Ivan Klabučar"
date: "12/14/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
habits = read.csv("data_health_and_prevention.csv")
head(habits)
```

```{r}
library('knitr')
library('tidyverse')
habits = habits[habits["DataValueTypeID"] == "AgeAdjPrv",]
preventions = habits[habits["Category"] == "Prevention", c("Measure", "Short_Question_Text")] %>% distinct()
kable(preventions, caption = "Possible preventions")
illnesses = habits[habits["Category"] == "Health Outcomes", c("Measure", "Short_Question_Text")] %>% distinct()
kable(illnesses, caption = "Possible illnesses")
```

Istražimo postoji li mjera preventivne zaštite koja je popularnija u saveznoj državi Ohio nego u saveznoj državi Florida.

```{r}
chol_screening_Ohio = habits[habits["StateDesc"] == "Ohio" & habits["Short_Question_Text"] == "Cholesterol Screening","Data_Value"]
chol_screening_Florida = habits[habits["StateDesc"] == "Florida" & habits["Short_Question_Text"] == "Cholesterol Screening","Data_Value"]
str_interp("Ohio Chol screening mean: $[.2f]{mean(chol_screening_Ohio)}, Florida chol screening mean: $[.2f]{mean(chol_screening_Florida)}")
```
No evidance that Cholesterol screening is more popular in Ohio.




```{r}
checkup_Ohio = habits[habits["StateDesc"] == "Ohio" & habits["Short_Question_Text"] == "Annual Checkup","Data_Value"]
checkup_Florida = habits[habits["StateDesc"] == "Florida" & habits["Short_Question_Text"] == "Annual Checkup","Data_Value"]

str_interp("Ohio annual checkup mean: $[.2f]{mean(checkup_Ohio)}, Florida annual checkup mean: $[.2f]{mean(checkup_Florida)}")
```
There is evidence that annual checkups are more popular in Ohio.
```{r}
t.test(checkup_Ohio, checkup_Florida, alt = "greater", var.equal = FALSE)
```
However that evidence is not significant at 0.05 confidence level.




```{r}
bpmed_Ohio = habits[habits["StateDesc"] == "Ohio" & habits["Short_Question_Text"] == "Taking BP Medication","Data_Value"]
bpmed_Florida = habits[habits["StateDesc"] == "Florida" & habits["Short_Question_Text"] == "Taking BP Medication","Data_Value"]

str_interp("Ohio blood pressure med mean: $[.2f]{mean(bpmed_Ohio)}, Florida blood pressure med mean: $[.2f]{mean(bpmed_Florida)}")
```
There is evidence that taking blood pressure medication is more popular in Ohio.
```{r}
t.test(bpmed_Ohio, bpmed_Florida, alt = "greater", var.equal = FALSE)
```
Taking blood pressure medication is significantly more popular in Ohio than Florida at 0.001 confidence level.



```{r}
insurance_Ohio = 100 - habits[habits["StateDesc"] == "Ohio" & habits["Short_Question_Text"] == "Health Insurance","Data_Value"]
insurance_Florida = 100 - habits[habits["StateDesc"] == "Florida" & habits["Short_Question_Text"] == "Health Insurance","Data_Value"]

str_interp("Ohio insurance mean: $[.2f]{mean(insurance_Ohio)}, Florida insurance mean: $[.2f]{mean(insurance_Florida)}")
```
There is evidence that health insurance is more popular in Ohio that in Florida.
```{r}
t.test(insurance_Ohio, insurance_Florida, alt = "greater", var.equal = FALSE)
```
Health insurance is significantly more popular in Ohio than in Florida at 0.005 confidence level. 


```{r}
COPD_data = habits[(habits["StateDesc"] == "Illinois" | habits[habits["StateDesc"] == "Iowa" | habits[habits["StateDesc"] == "South Dakota"),c("Data_Value", "PopulationCount", "Short_Question_Text")]
COPD_data = COPD_data[COPD_data["Short_Question_Text"] == "COPD", ]
```

